Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-24 submission5/core.tex
Whitespace

\ifcameraready
\author{
  \IEEEauthorblockN{
    Sean Noble Anderson
  }
  \IEEEauthorblockA{
    Portland State University\\
    ander28@pdx.edu\\
  }
  \and
  \IEEEauthorblockN{
    Roberto Blanco
  }
  \IEEEauthorblockA{
    Max Planck Institute for Security and Privacy\\
    roberto.blanco@mpi-sp.org\\
  }
  \and
  \IEEEauthorblockN{
    Leonidas Lampropoulos
  }
  \IEEEauthorblockA{
    University of Maryland, College Park\\
    leonidas@umd.edu\\
  }
  \linebreakand
  \IEEEauthorblockN{
    Benjamin C. Pierce
  }
  \IEEEauthorblockA{
    University of Pennsylvania\\
    bcpierce@cis.upenn.edu\\
   }
  \and
  \IEEEauthorblockN{
    Andrew Tolmach
  }
  \IEEEauthorblockA{
    Portland State University\\
    tolmach@pdx.edu\\
  }
}
\fi

@@

\begin{figure*}
  \begin{subfigure}{0.4\textwidth}
    \judgmentbr{\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap \unsealed(V)\)}
               {\(V' = V \llbracket \addr \mapsto \object \mid \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{f} ~ (\mathit{off, sz})) ~ (V,\sigma) = (V',\sigma)\)}

    \judgmentbr{\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap
                 \unsealed(V)\)}
               {\(V' = V \llbracket \addr \mapsto \public \mid \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{t} ~ (\mathit{off, sz})) ~ (V,\sigma) = (V',\sigma)\)}

    \judgmentbr{\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap \object(V)\)}
               {\(V' = V \llbracket \addr \mapsto \unsealed | \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{dealloc} ~ (\mathit{off, sz})) ~ (V,\sigma) = (V',\sigma)\)}

    \caption{Memory Allocation}
    \label{sfig:publicalloc}
  \end{subfigure}
  \begin{subfigure}{0.6\textwidth}
    %
    \[\mathit{push} ~ V ~ \overline{\reg} ~ K \triangleq \lambda k .
    \begin{cases}
      \unsealed & \textnormal{if } k \in CLR \\
      \public & \textnormal{if } k \in \overline{\reg_{\mathit{args}}} \\
      \sealed & \textnormal{if } k \in \WORDS \textnormal{ and } \\
      & k \in \object(V) - \components \\
      V(k) & \textnormal{otherwise} \\
    \end{cases}      
    \]
    %
    \[\mathit{passed} ~ \overline{sa} ~ \mach \triangleq \bigcup_{(\reg,\mathit{off},\mathit{sz}) \in \overline{sa}}
    \mathit{range} ~ \reg ~ \mathit{off} ~ \mathit{sz} ~ \mach\]
    %
    \judgmenttwo[\sc Call]
        {\(\components = \mathit{passed} ~ \overline{sa} ~ \mach\)}
        {\(V' = \mathit{push} ~ V ~ \overline{\reg_{args}} ~ \components\)}
        {\(Op ~ \mach ~ (\mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa})
          ~ (V,\sigma) = (V',V::\sigma)\)}
    %
    \judgmenttwo[\sc Tailcall]
        {\(\components = \mathit{passed} ~ \overline{sa} ~ \mach\)}
        {\(V' = \mathit{push} ~ V ~ \overline{\reg_{args}} ~ \components\)}
        {\(Op ~ \mach ~ (\mathbf{tail call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa})
          ~ (V,\sigma) = (V',\sigma)\)}

@@

For LTC, the original micro-policy, implemented as {\em PER\_DEPTH\_TAG},
fails in testing, in cases where data is leaked between sequential calls.
To round out our mutation testing we also check {\em LOAD\_NO\_CHECK\_LT},
equivalent to its counterpart in depth isolation,
and a version where stores succeed but fails to propagate the PC tag, {\em STORE\_NO\_UPDATE}.
It turns out that {\em PER\_DEPTH\_TAG} is a comparatively subtle bug,
taking longer to catch.

%% I don't think this discussion is relevant here
%% Unfortunately, Lazy Per-activation Tagging and Clearing
%% puts severe pressure on the tag cache, so it may not be usable in practice.
%% However, we conjecture that no lazy scheme can be fully stack safe
%% without using unique per-activation identifiers.

>>>>

\ifcameraready
\author{
  \IEEEauthorblockN{
    Sean Noble Anderson
  }
  \IEEEauthorblockA{
    Portland State University\\
    ander28@pdx.edu\\
  }
  \and
  \IEEEauthorblockN{
    Roberto Blanco
  }
  \IEEEauthorblockA{
    MPI-SP\\
    roberto.blanco@mpi-sp.org\\
  }
  \and
  \IEEEauthorblockN{
    Leonidas Lampropoulos
  }
  \IEEEauthorblockA{
    University of Maryland, College Park\\
    leonidas@umd.edu\\
  }
  \linebreakand
  \IEEEauthorblockN{
    Benjamin C. Pierce
  }
  \IEEEauthorblockA{
    University of Pennsylvania\\
    bcpierce@cis.upenn.edu\\
   }
  \and
  \IEEEauthorblockN{
    Andrew Tolmach
  }
  \IEEEauthorblockA{
    Portland State University\\
    tolmach@pdx.edu\\
  }
}
\fi

@@

\begin{figure*}
  \begin{subfigure}{0.48\textwidth}
    \judgmentbr[~AllocF]
        {\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap \unsealed(V)\)}
        {\(V' = V \llbracket \addr \mapsto \object \mid \addr \in \components \rrbracket\)}
        {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{f} ~ (\mathit{off, sz})) ~ (V,\sigma) = (V',\sigma)\)}

    \judgmentbr[~AllocT]
               {\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap
                 \unsealed(V)\)}
               {\(V' = V \llbracket \addr \mapsto \public \mid \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{t} ~ (\mathit{off, sz})) ~ (V,\sigma) = (V',\sigma)\)}

    \judgmentbr[~Dealloc]
        {\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap \object(V)\)}
        {\(V' = V \llbracket \addr \mapsto \unsealed | \addr \in \components \rrbracket\)}
        {\(Op ~ \mach ~ (\mathbf{dealloc} ~ (\mathit{off, sz})) ~ (V,\sigma) = (V',\sigma)\)}

    \caption{Memory Allocation}
    \label{sfig:publicalloc}
  \end{subfigure}
  \begin{subfigure}{0.52\textwidth}
    %
    \[\mathit{push} ~ V ~ \overline{\reg} ~ K \triangleq \lambda k .
    \begin{cases}
      \unsealed & \textnormal{if } k \in CLR \\
      \public & \textnormal{if } k \in \overline{\reg_{\mathit{args}}} \\
      \sealed & \textnormal{if } k \in \WORDS \textnormal{ and } \\
      & k \in \object(V) - \components \\
      V(k) & \textnormal{otherwise} \\
    \end{cases}      
    \]
    %
    \[\mathit{passed} ~ \overline{sa} ~ \mach \triangleq \bigcup_{(\reg,\mathit{off},\mathit{sz}) \in \overline{sa}}
    \mathit{range} ~ \reg ~ \mathit{off} ~ \mathit{sz} ~ \mach\]
    %
    \judgmenttwo[~Call]
        {\(\components = \mathit{passed} ~ \overline{sa} ~ \mach\)}
        {\(V' = \mathit{push} ~ V ~ \overline{\reg_{args}} ~ \components\)}
        {\(Op ~ \mach ~ (\mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa})
          ~ (V,\sigma) = (V',V::\sigma)\)}
    %
    \judgmenttwo[~Tailcall]
        {\(\components = \mathit{passed} ~ \overline{sa} ~ \mach\)}
        {\(V' = \mathit{push} ~ V ~ \overline{\reg_{args}} ~ \components\)}
        {\(Op ~ \mach ~ (\mathbf{tail call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa})
          ~ (V,\sigma) = (V',\sigma)\)}

@@

For LTC, the original micro-policy, implemented as {\em PER\_DEPTH\_TAG},
fails in testing, in cases where data is leaked between sequential calls.
To round out our mutation testing we also check {\em LOAD\_NO\_CHECK},
equivalent to its counterpart in depth isolation,
and a version where stores succeed but fails to propagate the PC tag, {\em STORE\_NO\_UPDATE}.
It turns out that {\em PER\_DEPTH\_TAG} is a comparatively subtle bug,
taking longer to catch.
